Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance

### 2017-08-10 ms_pre_post.Rmd
Minor wording tweaks

---
title: Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance
  and associated polyandry
author: ''
date: "3 August 2017"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

We restricted our current model to examine how reproductive strategy evolution was affected by direct costs and indirect benefits stemming from inbreeding avoidance, thereby isolating such effects and explicitly addressing key general hypotheses regarding the effects of inbreeding depression. In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes'). Future investigations could consequently model multiple benefits and costs of reproductive strategies, and be parameterised using empirical data. The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.

>>>>

---
title: Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance
  and associated polyandry
author: ''
date: "10 August 2017"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

We restricted our current model to examine how reproductive strategy evolution was affected by direct costs and indirect benefits stemming from inbreeding avoidance, thereby isolating such effects and explicitly addressing key general hypotheses regarding the effects of inbreeding depression. In natural populations, reproductive strategy evolution will also be affected by other costs and benefits, for example, stemming from additive genetic effects (i.e., pre-copulatory or post-copulatory mate choice for 'good genes'). Future investigations could consequently be to develop theory and models that include multiple benefits and costs of reproductive strategies, which could then be parameterised using empirical data. While good theory should always strive for conceptual clarity and the avoidance of unnecessary nuance [@Healy2017], the prudent use of multi-faceted mechanistic models could usefully link theory, modelling, and empirical hypothesis testing and thereby improve both general and specific understanding and prediction of reproductive strategy evolution.
